\documentclass[12pt]{elsarticle}
\pdfoutput=1

%% Useful packages
\usepackage{amsmath,mathtools,latexsym,amssymb,bm}
\usepackage{graphics}
\usepackage{fullpage,lineno,soul,url,ulem}
\usepackage{natbib}

\renewcommand{\baselinestretch}{1.5}
\renewcommand{\figurename}{Fig.}

\journal{Ecologicall Modelling}

\usepackage[colorlinks=true, urlcolor=blue, linkcolor=red, citecolor=green,
            plainpages=false,
            pdftex,
            pdftitle={The relationship between confidence intervals and distributions of estimators for parameters of deterministic models},
            pdfauthor={Dina Lika,  Bas Kooijman},
            pdfsubject={parameter distribution},
            pdfkeywords={parameter interval}]{hyperref}
\begin{document}

\title{Supporting Information: The relationship between confidence intervals and distributions of estimators for parameters of deterministic models}

\author{Konstadia Lika$^{1,2}$, 
        Sebastiaan A.L.M. Kooijman$^{3\ast}$}
  
\bigskip

\address{$^1$ Department of Biology, University of Crete, 70013, Heraklion, Greece}
\address{$^2$ Institute of Computational Mathematics,
Foundation of Research and Technology Hellas, 70013 Heraklion, Greece}
\address{$^3$  Amsterdam Institute for Life and Environment (A-LIFE), 
VU University Amsterdam, de Boelelaan 1087, 1081 HV, The Netherlands}
\address{$^\ast$ Corresponding author: bas.kooijman@vu.nl}

\date{2024/01/27}


\maketitle
% \listoffigures 

\section{Supporting Information}

In this document the code used generating each of the 13 figures is listed. The code works Matlab\textsuperscript{\textcopyright} and with free open source DEBtool\_M software - \url{https://debtool.debtheory.org/docs/index.html}.

Code was run with Matlab\textsuperscript{\textcopyright} R2021a. 

\begin{itemize}
    \item mydata\_F2S\_exp.m - From loss function to survivor function for the exponential model. Calls exprnd.m and exponential.m
    \item mydata\_F2S\_wbl.m - From loss function to survivor function for the Weibull model. Calls wblrnd.m and weibull.m 
    \item mydata\_Ssb\_exp.m - Compares SB-estimates for parameters of exponential distribution based on fitting exp$(-\lambda \, t)$ for 2 definitions of empirical survival data. Calls exprnd.m and exponential.m
    \item mydata\_Ssb\_wbl.m - Compares SB and ML-estimates for parameters of the Weibull distribution based on fitting exp$(-\lambda \, t)^k$. Calls wblrnd.m and weibull.m 
    \item mydata\_F2S\_vBert.m - Generates figures 11 and 12 . Calls vBert.m and generates  vBert.mat and/or else loads those data.
    \item mydata\_F2S\_vBert\_2D.m  - Generates figures 13. Calls vBert.m and either generates .mat files vBert\_2D.mat and vBert.mat or else loads those data. vBert\_2D.mat and vBert.mat are in the folder which enables the function to execute fast. User can un-comment relevant parts of the code to re-generate the data. 
\end{itemize}









\end{document}
