\documentclass{article}

\usepackage{a4wide,bm,graphicx,url,color,longtable,caption}
%\usepackage{natbib}
\usepackage[sort&compress,comma,authoryear]{natbib}
\usepackage{apalike,lineno,ulem}
\renewcommand{\baselinestretch}{1.5}

\begin{document}
\captionsetup{width=15cm}

\title{Supporting Tables from: The comparative energetics of the turtles and crocodiles
\footnote{Ecology and Evolution 12(6): e8996; doi: 10.1002/ece3.8996.}}

\author{
       Nina Marn,
       Sebastiaan A.L.M. Kooijman 
       }

\date{April 2022, doi: 10.1002/ece3.8996}

\maketitle

% Table A.1 with Species 
{\footnotesize\begin{longtable}[c]{p{3.5cm}p{5.5cm}p{5.5cm}} 
\caption{\label{tab:species}\protect\small
Testudines and Crocodilia species that are included in the AmP collection at 2021/10/02, the data types as extracted from the literature and selected references.
Data were also obtained from websites, which are presented in the AmP website for each entry. The codes of the data types are presented in Table~\ref{tab:codes}.} \\

\hline
\textbf{species} & \textbf{data} & \textbf{references} \\ \hline
\hline
\endfirsthead

\hline
\multicolumn{3}{|c|}{Continuation of Table \ref{tab:species}} \\ 
\hline
\textbf{species} & \textbf{data} & \textbf{references} \\ 
\hline
\endhead

Actinemys marmorata &  am, Lp, Li, Wwb, Wwi, Ri, t-L & \citet{GermRied2015} \\
Aldabrachelys gigantea &  ab, ap, am, Lb, Lp, Li, Wwb, Wwp, Wwi, Ri & \citet{ErnsBarb1989} \\
Alligator mississippiensis &  ab, ap, am, Lp, Li, Ww0, Wwi, Ri, t-L & \citet{DeemFerg1991,JacoKush1989} \\
Alligator sinensis &  ab, ap, am, Lp, Li, Ww0, Wwb, Wwi, Ri, t-L, t-Ww & \citet{HerbCoul2002} \\
Apalone mutica &  am, Lp, Li, Wwb, Wwi, t-L, L-N & \citet{Plum1977} \\
Apalone spinifera &  ab, ap, am, Lb, Lp, Li, Wwb, Wwi, Ri, t-L, L-dL & \citet{PlumMill2015} \\
Astrochelys yniphora &  ab, am, Lb, Lp, Li, Wwp, Wwi, Ri, L-dL & \citet{SmitPedr2001} \\
Batagur affinis &  ab, ap, am, Lb, Lp, Li, Ww0, Wwb, Wwi, Ri, t-Ww, t-L & \citet{MollPlatt2015,HairShah2014} \\
Batagur baska &  ab, ap, am, Wwb, Wwi, Ri, t-Ww & \citet{WeisPrei2015} \\
Caiman crocodilus &  ab, ap, am, Lb, Lp, Li, Ww0, Wwi, Ri, t-L & \citet{MiraMora2002,CampMour2014,CampMagn2008} \\
Caiman latirostris &  ab, ap, am, Lp, Li, Wwb, Wwi, Ri, t-L & \citet{ViotNava2020} \\
Caiman yacare &  ap, am, Lb, Lp, Li, Wwb, Wwi, Ri, t-L & \citet{CampMour2014} \\
Caretta caretta &  ah, ab, ap, am, Lh, Lb, Lp, Li, Wwh, Wwb, Wwp, Wwi, Ri, E0, T-ah, t-L\_T, t-Ww\_T, L-Ww, L-N, L-dL, L0-Lt & \citet{StokWyne2006,GodfMros1997,Stok2014,Spot2004,ZugWynn1986,ReicBjor2008,ByrdMurp2005,EhrhYode1978,Ston1980,Nort2005,TiwaBjor2000,HaysSpea1991,MillLimp2003,Tuck2010,HawkBrod2005,Park1926,Park1929,HildHats1927,WabnPaul2008,BjorBolt2000,SnovAven2007,ScotMars2012,BjorSchr2013,BrauEppe2008} \\
Caretta caretta MED &  ah, ab, ap, am, Lb, Lp, Li, Wwb, Wwp, Wwi, Ri, E0, T-ah, t-L\_fT, t-Ww\_T, L-Ww, L-N & \citet{ReidMarg2009,GodfMros1997,Stok2014,CasaCont2011,PiovClus2011,MargArga2003,Groom1990,TiwaBjor2000,HaysSpea1991,BrodGlen2003,ZbinMarg2006,Cate2014,CasaPino2009,MarnJusu2018} \\
Carettochelys insculpta &  ap, am, Lb, Lp, Li, Wwb, Wwp, Wwi, Ri, t-WwVe, t-JOe, t-WwYe & \citet{DoodGeor2003,WebbChoq1986} \\
Centrochelys sulcata &  ap, am, Wwb, Wwi, Ri, t-Ww, L-Ww & \citet{RitzGrieb2010} \\
Chelodina oblonga &  ab, ap, am, Lb, Lp, Li, Wwb, Ri, L-dL, t-L, L-Ww & \citet{ErnsBarb1989,Kenn1996} \\
Chelonia mydas &  ah, ab, ap, am, Lh, Lp, Li, Wwh, Wwp, Wwi, Ri, E0, T-ah, t-WwYe\_T, t-WwVe\_T, t-JOe\_T, t-JCe\_T, L0-Lt, L-Ww & \citet{BalaRoss1974,Chri1990,Hend1958,PereBoot2011,SalmHama2009,BalaChal2004,BellPars2005,ChalLimp2004,FrazEhrh1985,FrazLadn1986,GoshAven2010,VanHHarg2014,ZuriHerr2012,Prin2017,MoreBapt1995,VenkKann2005,Wine2016,RuslBoot2016,BjorCarr1989,BrodGlen2003,EkanKapu2016,Guin2009,Limp1993,Limp2009,LimpMill2003,LimpNich1988,TroeChal2007} \\
Chelonoidis niger &  ab, ap, am, Lb, Li, Wwb, Wwi, Ri, t-Ww & \citet{RitzHamm2010} \\
Chelus fimbriata &  ab, am, Lb, Lp, Li, L\_t, Wwb, Wwi, Ww\_t, Ri, t-L & \citet{Prit2008} \\
Chelydra serpentina &  ap, am, Lp, Li, Wwb, Wwi, Ww\_L, Ri, t-Ww, T-a\_b & \citet{WilliSpot1989,Ynte1978} \\
Chrysemys picta &  ab, ap, am, Li, Wwb, Ri, t-L, t-Ww & \citet{Rowe1994,Wilb1975} \\
Claudius angustatus &  ab, ap, am, Lb, Lp, Li, Wwb, Wwp, Wwi, Ri & \citet{LeglVogt2013} \\
Clemmys guttata &  ab, ap, am, Lb, Lp, Li, Wwi, Ri, t-L & \citet{Erns1975} \\
Crocodylus acutus &  ab, ap, am, Lb, Lp, Li, Wwb, Wwi, Ri, L0-Lt, L-Ww & \citet{GarcBuen2012} \\
Crocodylus intermedius &  ap, am, Lb, Lp, Li, Wwi, Ri, t-L & \citet{Seij2016} \\
Crocodylus johnsoni &  ab, ap, am, Lb, Lp, Li, Wwb, Wwp, Wwi, Ri, t-WwYe, t-WwVe, t-JOe & \citet{Whit1987,WhitWebb1990} \\
Crocodylus mindorensis &  ab, ap, am, Lp, Li, Wwb, Wwp, Wwi, Ri & \citet{MarzRuss2014} \\
Crocodylus moreletii &  ab, ap, am, Lb, Lp, Li, Wwb, Wwi, Ri, L0-Lt, L-Ww & \citet{PereRang1995} \\
Crocodylus niloticus &  ab, ap, am, Lb, Lp, Li, Wwb, Wwp, Wwi, Ri, L-Ww & \citet{NgwePatz2013} \\
Crocodylus palustris &  ab, ap, am, Lb, Lp, Li, Wwb, Wwi, Ri & \\
Crocodylus porosus &  ab, ap, am, Lb, Lp, Li, Wwb, Wwp, Wwi, Ri, L-Ww & \citet{Brie2015} \\
Crocodylus rhombifer &  ab, ap, am, Lp, Li, Wwb, Wwi, Ri & \citet{TargSobe2010} \\
Crocodylus siamensis &  ab, ap, am, Lb, Lp, Li, Wwi, Ri, L-Ww & \citet{PlatNomy2012,ChenHugg1983} \\
Cuora flavomarginata &  ab, ap, am, Lb, Lp, Li, Wwb, Wwp, Wwi, Ri, t-L & \citet{ChenLue2002} \\
Deinosuchus rugosus &  ap, am, Li, Wwi, Ri, t-L & \citet{EricBroc1999} \\
Deirochelys reticularia &  ab, ap, am, Lb, Lp, Li, Wwb, Wwi, Ri, t-L & \citet{BuhlCond2009} \\
Dermatemys mawii &  ab, ap, am, Lb, Lp, Li, L\_t, Wwb, Wwp, Wwi, Ww\_t, Ri & \citet{LeglVogt2013} \\
Dermochelys coriacea &  ab, ap, am, Lb, Lp, Li, Wwb, Wwi, Ri, JXi, pAi, t-L\_f, t-Ww & \citet{Jone2009} \\
Elseya albagula &  ab\_T, ap, am, Lb, Lp, Li, Ww0, Wwi, Ri, t-L & \citet{Limp2008} \\
Elseya dentata &  ab, ap, am, Lb, Lp, Li, Wwb, Wwp, Wwi, Ri, L-dL, t-L & \citet{ErnsBarb1989,Kenn1996} \\
Elusor macrurus &  ab, ap, am, Lb, Lp, Li, Wwi, Ri, t-L & \citet{Limp2008} \\
Emydoidea blandingii &  ab, ap, am, Lb, Li, Wwb, Wwi, Ri, t-L, t-Ww & \citet{CongLobe1991} \\
Emydura macquarii &  ab\_T, ap, am, Lb, Lp, Li, Wwb, Wwp, Wwi, Ri, t-L & \citet{Spen2002} \\
Emydura victoriae &  ab, ap, am, Wwb, Wwi, Ri, t-Ww & \citet{GaikClar2011,Jone2003} \\
Emys orbicularis &  ab, ap, am, Lb, Lp, Li, Wwb, Ri, t-L, t-Ww & \citet{MasiFice2015} \\
Eretmochelys imbricata &  ab, ap, am, Lb, Li, Wwb, Wwi, Ri, t-L & \citet{Witz1980,BellPike1980} \\
Gavialis gangeticus &  ab, ap, am, Lb, Lp, Li, L\_t, Ww0, Wwb, Wwi, R\_L & \\
Geochelone elegans &  ab, ap, am, Lb, Li, Ww0, Wwb, Wwi, Ri, t-Ww, t-L & \citet{Vyas1997} \\
Glyptemys insculpta &  ab, ap, am, Lb, Lp, Li, Wwb, Wwi, Ri, t-L & \citet{MarcHugh2018} \\
Glyptemys muhlenbergii &  ab, ap, am, Lb, Lp, Li, Wwi, Ri, t-L & \citet{LoviErns1998} \\
Gopherus agassizii &  ab, ap, am, Lb, Lp, Li, Wwb, Wwp, Wwi, Ri, t-L & \citet{MediNuss2012,ErnsBarb1989} \\
Gopherus berlandieri &  ab, ap, am, Lb, Li, Wwb, Ri, t-Ww, t-L & \citet{JuddMcQu1980} \\
Gopherus morafkai &  ab, ap, am, Lb, Lp, Li, Wwb, Wwi, Ri, t-L & \citet{Brid2012,AverChri2018} \\
Gopherus polyphemus &  ab, ap, am, Lb, Lp, Li, Wwb, Wwp, Wwi, Ri, t-L & \citet{MushWils1994,ErnsBarb1989} \\
Graptemys caglei &  ab, ap, am, Lb, Li, Wwi, Ri, t-L & \citet{Lind1999} \\
Graptemys ernsti &  ab, ap, am, Lb, Li, Wwi, Ri, t-L & \citet{Lind1999} \\
Graptemys oculifera &  ab, ap, am, Lb, Li, Wwb, Wwi, Ri, t-L & \citet{JoneHart1995} \\
Graptemys ouachitensis &  ab, am, Lb, Lp, Li, Wwi, Ri, t-L & \citet{Lind1999} \\
Graptemys pseudogeographica &  ab, am, Lb, Lp, Li, Wwi, Ri, L-r & \citet{Webb1961} \\
Graptemys versa &  ab, ap, am, Lb, Lp, Li, Wwi, t-L, L-N & \citet{Lind2005} \\
Heosemys spinosa &  ab, am, Lb, Lp, Li, Ww0, Wwb, Wwi, Ri, t-Ww, L-Ww & \citet{Goet2007} \\
Homopus signatus &  ab, ap, am, Lb, Lp, Li, Wwb, Wwi, Ri, L-dL & \citet{Loeh2004} \\
Hydromedusa maximiliani &  ab, ap, am, Lb, Lp, Li, Wwb, Wwi, Ri, L-dL & \citet{MartSouz2008,NoveSous2008} \\
Kinosternon flavescens &  ab, ap, am, Lb, Li, Wwi, Ri, t-L, Ww-WwR & \citet{Iver1991} \\
Kinosternon hirtipes &  ab, ap, am, Lb, Li, Wwi, Ri, t-L & \citet{IverBart1991} \\
Kinosternon scorpioides &  ab, am, Lb, Lp, Li, Ww0, Wwi, Ri, t-L, t-Le & \citet{BragFern2021,Iver2010} \\
Kinosternon sonoriense &  am, Lb, Lp, Li, Wwb, Wwi, Ri, t-L & \citet{HensJone2010} \\
Kinosternon subrubrum &  ab, ap, am, Lb, Li, Wwi, Ri, t-L, L-Ww & \citet{Iver1979} \\
Lepidochelys kempii &  ab, ap, am, Lb, Lp, Li, Wwb, Wwp, Wwi, Ri & \citet{Spot2004} \\
Lepidochelys olivacea &  ab, ap, am, Wwb, Wwp, Wwi, Ri, t-Ww & \citet{MarkKirk1988} \\
Macrochelys temminckii &  ab, ap, am, Lb, Lp, Li, Wwp, Wwi, Ri, t-L & \citet{Dobi1971} \\
Malaclemys terrapin &  ab\_T, ap, am, Wwb, Wwi, Ri, t-Ww\_T & \citet{RoosKell1996} \\
Malacochersus tornieri &  ab, ap, am, Lb, Li, L\_t, Wwb, Wwi, Ww\_t, Ri & \citet{EwerHatc2004} \\
Mauremys japonica &  ap, am, Lb, Lp, Li, Wwb, Wwi, Ri, t-L & \citet{Yabe1989} \\
Mauremys reevesii &  ab, am, Wwb, Wwp, Wwi, Ri, t-Ww & \citet{DuShen2009} \\
Mauremys rivulata &  ab, ap, am, Lb, Lp, Li, Wwi, Ri, t-L & \citet{CiceKuma2016} \\
Mauremys sinensis &  ap, am, Lb, Lp, Li, Wwb, Wwp, Wwi, Ri, t-L & \citet{ChenLue1998} \\
Mecistops cataphractus &  ab, ap, am, Lp, Li, Ww0, Wwb, Wwi, Ri &  \\
Melanochelys tricarinata &  ap, am, Lb, Lp, Li, Wwb, Wwi, Ri, t-L, L-Ww & \citet{KumaHari2010} \\
Melanosuchus niger &  ab, am, Lp, Li, Wwb, Wwi, Ri, L-L & \citet{Herr1991} \\
Myuchelys bellii &  ab, ap, am, Lb, Lp, Li, Ww0, Wwi, Ri, t-L & \citet{FielLimp2015} \\
Natator depressus &  ah, ab, ap, am, Lh, Lb, Lp, Li, Ww0, Wwh, Wwp, Wwi, Ri, E0, T-ah, L0-Lt, L-Ww, t-Ww & \citet{Bent2017,Limp2007,WaayStub2016,DBCA2019,VenkKann2005,Wine2016,RuslBoot2016,StubMitc2019,Salm2017} \\
Osteolaemus tetraspis &  ab, ap, am, Lp, Li, Ww0, Wwb, Wwi, Ri &  \\
Paleosuchus palpebrosus &  ab, ap, am, Lb, Lp, Li, Wwb, Wwi, Ri, t-L & \citet{CampMahn2013} \\
Paleosuchus trigonatus &  ab, ap, am, Lp, Li, Wwb, Wwi, Ri, t-L, t-Ww &  \\
Pangshura tecta &  ab, ap, am, Lb, Lp, Li, Wwb, Wwi, Ri, t-L, t-Ww & \citet{Vyas1979} \\
Pelodiscus sinensis &  am, Lp, Li, Wwb, Wwi, Ri, t-Ww, T-ab & \citet{JiChen2003} \\
Pelomedusa subrufa &  ab, ap, am, Lb, Lp, Li, Wwb, Wwp, Wwi, L-N & \citet{Stry2001} \\
Pelusios castanoides &  ab, ap, am, Lb, Lp, Li, Wwp, Wwi, Ri, t-L & \citet{Gerl2008} \\
Pelusios subniger &  ab, ap, am, Lb, Lp, Li, Wwp, Wwi, Ri, t-L & \citet{Gerl2008} \\
Platysternon megacephalum &  ab, ap, am, Lp, Li, Wwb, Ri, L-Ww & \citet{SungHau2014,SungHau2015} \\
Podocnemis expansa &  ab, ap, am, Lb, Lp, Li, Wwb, Wwp, Wwi, Ri, t-L\_e, t-L & \citet{MagaVogt2017,ChinVale2008} \\
Podocnemis lewyana &  ap, am, Lb, Lp, Li, Wwb, Wwi, Ri, L-dL, T-ab & \citet{PaezBock2015,PaezCorr2009} \\
Podocnemis unifilis &  ab, ap, am, Lb, Lp, Li, Wwb, Wwp, Wwi, Ri, t-L\_f, t-Ww\_f & \citet{MeerRobi2016,MiorGiar2016} \\
Psammobates geometricus &  ab, ap, am, Lb, Lp, Li, Wwi, Ri, L-dL & \citet{Baar1995} \\
Psammobates oculiferus &  am, Lb, Lp, Li, Wwp, Ri, t-L, t-Ww & \citet{Kesw2012} \\
Pseudemydura umbrina &  ab, ap, am, Lb, Lp, Li, Wwb, Wwp, Wwi, Ri, L-Ww, t-L\_f, t-Ww\_f, T-JO & \citet{Arna2018,BurbKuch2010,Burb1981,ArnaKuch2015} \\
Pseudemys alabamensis &  ab, ap, am, Lb, Li, Ri, t-L, L-Ww & \citet{Grah1971} \\
Pseudemys concinna &  ab, ap, am, Lb, Li, Wwb, Wwi, Ri, t-L & \citet{Dres1997} \\
Pseudemys nelsoni &  ab, ap, am, Lb, Li, Wwb, Wwi, Ri, L0-Lt & \citet{MunsWald2015} \\
Pseudemys peninsularis &  ap, am, Lb, Li, Wwi, Ri, L0-Lt & \citet{MunsWald2015} \\
Pseudemys texana &  ab, ap, am, Lb, Lp, Li, Wwi, Ri, t-L & \citet{Lind2007} \\
Rhinemys rufipes &  ab, ap, am, Lb, Lp, Li, Wwp, Wwi, Ri, L0-Lt & \citet{MagnLima1997} \\
Sternotherus depressus &  ab, ap, am, Lb, Li, Wwi, Ri, L-r & \citet{MelaAngu2011} \\
Sternotherus minor &  ab, ap, am, Lb, Lp, Li, Wwb, Wwi, Ri, L-r & \citet{Beck2003,CoxHaze1991} \\
Sternotherus odoratus &  ab, ap, am, Lb, Li, Wwi, Ri, t-L & \citet{Erns1986} \\
Stigmochelys pardalis &  ab, ap, am, Li, Wwb, Wwi, Ri, t-Ww, L-Ww & \citet{RitzHamm2010} \\
Terrapene carolina &  ab, ap, am, Lb, Lp, Li, Wwi, Ri, t-L & \citet{ErnsWilg1998} \\
Terrapene ornata &  ab, ap, am, Lb, Li, Wwi, Ri, t-L, L-Ww & \citet{SkorAnde2021} \\
Testudo graeca &  ab\_T, ap, am, Wwb, Ri, t-Ww & \citet{HichZnar2016,RitzClau2012} \\
Testudo hermanni &  ab, ap, am, Lp, Li, Wwb, Wwi, Ri, t-Ww & \citet{RitzClau2012} \\
Tomistoma schlegelii &  ab, ap, am, Lp, Li, Ww0, Wwi, Ri & \\
Trachemys scripta &  ab, ap, am, Lb, Li, Wwb, Wwi, Ri, t-L & \citet{FrazGibb1990} \\
Trionyx triunguis &  am, Lp, Li, Ww0, Wwb, Wwi, Ri, t-Wwe, t-Wde, t-JOe & \citet{LeshAr1991} \\
\hline
\end{longtable}}

\clearpage
% ------------------------------------------------------------------

% Table A.2 with codes 
\begin{table}[h!]\small
\caption{\label{tab:codes}\protect\small
The codes of the data types as presented in Table \ref{tab:species}.
Zero variate data left, uni-variate data right.
Life history events: 0 start development, h hatch, b birth, p puberty, m death, i death.
T stands for temperature.}
\begin{tabular}{ll|ll} \hline
\textbf{code} & \textbf{description} & \textbf{code} & \textbf{description}\\ \hline
ah & age at h & t-Le & time, embryo length\\ 
ab & age at birth & t-L & time, length\\ 
ab\_T & age at birth (several T) & t-L\_T & time, length (several T)\\ 
ap & age (or time since birth) at p & t-L\_f & time, length (several f)\\ 
am & age at death (life span) & t-L\_fT & time, length (several f, T)\\ 
Lh & length at h & t-Wwe & time, embryo wet weight\\ 
Lb & length at b & t-WwYe & time, embryo yolk wet weight\\ 
Lp & length at p & t-WwVe & time, embryo wet weight excluding yolk\\ 
Li & length at i & t-Ww & time, wet weight\\ 
L\_t & length at time t & t-Ww\_f & time, wet weight (several f)\\ 
Ww0 & wet weight at 0 & t-Ww\_T & time, wet weight (several T)\\ 
Wwh & wet weight at h & t-Wde & time, embryo dry weight (total)\\ 
Wwb & wet weight at b & t-JOe & time, embryo O$_2$ consumption\\ 
Wwp & wet weight at p & t-JOe\_T & time, embryo O$_2$ cons (several T)\\ 
Wwi & wet weight at i & L-L & length, length (different length measures)\\ 
Ww\_L & wet weight at length & L-dL & length, change in length\\ 
Ww\_t & wet weight at time & L0-Lt & length at capture, length at recapture\\ 
E0 & reserve energy at 0 & L-Ww & length, wet weight\\ 
Ri & reproduction rate at i & L-r & length, specific growth rate\\ 
R\_L & reproduction rate at length & L-N & length, number of eggs/offspring\\ 
pAi & maximum assimilation rate (energy) & Ww-WwR & wet weight, clutch wet weight\\ 
JXi & food consumption at i & T-ah & temperature, age at h\\ 
  &   & T-ab & temperature, age at b\\ 
  &   & T-JO & temperature, O$_2$ consumption\\ 
\hline
\end{tabular}
\end{table}
\clearpage
\begin{thebibliography}{}

\bibitem[Arnall, 2018]{Arna2018}
Arnall, S. (2018).
\newblock unplublished data.

\bibitem[Arnall et~al., 2015]{ArnaKuch2015}
Arnall, S., Kuchling, G., and Mitchell, N. (2015).
\newblock A thermal profile of metabolic performance in the rare {A}ustralian
  chelid, \emph{Pseudemydura umbrina}.
\newblock {\em Australian Journal of Zoology}, 62:448--453.

\bibitem[Averill-Murray et~al., 2018]{AverChri2018}
Averill-Murray, R.~C., Christopher, T.~E., and Henen, B.~T. (2018).
\newblock Reproductive ecology and life history of female {S}onoran desert
  tortoises (\emph{Gopherus morafkai}).
\newblock {\em Herpetological Monographs}, 32(1):34--50.

\bibitem[Baard, 1995]{Baar1995}
Baard, E. H.~W. (1995).
\newblock Growth, age at maturity and sexual dimorphism in the geometric
  tortoise, \emph{Psammobates geometricus}.
\newblock {\em The Journal of the Herpetological Association of Africa},
  44(1):10--15.

\bibitem[Balazs and Chaloupka, 2004]{BalaChal2004}
Balazs, G. and Chaloupka, M. (2004).
\newblock Spatial and temporal variability in the somatic growth of green sea
  turtles \emph{Chelonia mydas} resident in the hawaiian archipelago.
\newblock {\em Marine Biology}, 145(5):1043--1059.

\bibitem[Balazs and Ross, 1974]{BalaRoss1974}
Balazs, G. and Ross, E. (1974).
\newblock Observations on the preemergence behaviour of the green turtle.
\newblock {\em Copeia}, 1974(4):986--988.

\bibitem[Becker, 2003]{Beck2003}
Becker, H. (2003).
\newblock Comments on keeping and breeding the loggerhead musk turtle,
  \emph{Sternotherus minor minor} ({A}gassiz, 1857).
\newblock {\em Radiata}, 12(1):3--10.

\bibitem[Bell et~al., 2005]{BellPars2005}
Bell, C., Parsons, J., Austin, T., Broderick, A., Ebanks-Petrie, G., and
  Godley, B. (2005).
\newblock Some of them came home: the cayman turtle farm headstarting project
  for the green turtle \emph{Chelonia mydas}.
\newblock {\em Oryx}, 39(2):137--148.

\bibitem[Bell and Pike, 1980]{BellPike1980}
Bell, I. and Pike, D.~A. (1980).
\newblock Somatic growth rates of hawksbill turtles \emph{Eretmochelys
  imbricata} in a northern {G}reat {B}arrier {R}eef foraging area.
\newblock {\em Marine Ecology Progress Series}, 446:275--283.

\bibitem[Bentley, 2017]{Bent2017}
Bentley, B. (2017).
\newblock Lab data collected at UWA, Perth by Blair Bentley.

\bibitem[Bjorndal and Carr, 1989]{BjorCarr1989}
Bjorndal, K. and Carr, A. (1989).
\newblock Variation in clutch size and egg size in the green turtle nesting
  population at torteguero, costa rica.
\newblock {\em Herpetologica}, 45(2):181--189.

\bibitem[Bjorndal et~al., 2000]{BjorBolt2000}
Bjorndal, K.~A., Bolten, A.~B., and Martins, H.~R. (2000).
\newblock Somatic growth model of juvenile loggerhead sea turtles
  \textit{Caretta caretta}: duration of pelagic stage.
\newblock {\em Marine Ecology Progress Series}, 202:265--272.

\bibitem[Bjorndal et~al., 2013]{BjorSchr2013}
Bjorndal, K.~A., Schroeder, B.~A., Foley, A.~M., Witherington, B.~E., Bresette,
  M., Clark, D., Herren, R.~M., Arendt, M.~D., Schmid, J.~R., Meylan, A.~B.,
  Meylan, P.~A., Provancha, J.~A., Hart, K.~M., Lamont, M.~M., Carthy, R.~R.,
  and Bolten, A.~B. (2013).
\newblock Temporal, spatial, and body size effects on growth rates of
  loggerhead sea turtles (\textit{Caretta caretta}) in the {N}orthwest
  {A}tlantic.
\newblock {\em Marine Biology}, 160(10):2711--2721.

\bibitem[Braun-Mc{N}eill et~al., 2008]{BrauEppe2008}
Braun-Mc{N}eill, J., Epperly, S.~P., Avens, L., Snover, M.~L., and Taylor,
  J.~C. (2008).
\newblock Growth rates of loggerhead sea turtles (\textit{Caretta caretta})
  from the western {N}orth {A}tlantic.
\newblock {\em Herpetological Conservation and Biology}, 3(2):273--281.

\bibitem[Bridges, 2012]{Brid2012}
Bridges, A. (2012).
\newblock {\em Sonoran Desert Tortoise (\emph{Gopherus morafkai}) Growth and
  Juvenile Habitat Selection at a Long-term Study Site in Central {A}rizona,
  {U}{S}{A}}.
\newblock PhD thesis, Arizona State University.

\bibitem[Brien, 2015]{Brie2015}
Brien, M.~L. (2015).
\newblock {\em Growth and survival of hatchling saltwater crocodiles
  (\emph{Crocodylus porosus}) in captivity: the role of agonistic and thermal
  behaviour}.
\newblock PhD thesis, Research Institute for the Environment and Livelihoods,
  Charles Darwin University.

\bibitem[Broderick et~al., 2003]{BrodGlen2003}
Broderick, A.~C., Glen, F., Godley, B.~J., and Hays, G.~C. (2003).
\newblock Variation in reproductive output of marine turtles.
\newblock {\em Journal of Experimental Marine Biology and Ecology},
  288:95--109.

\bibitem[Buhlmann et~al., 2009]{BuhlCond2009}
Buhlmann, K.~A., Congdon, J.~D., Gibbons, J.~W., and Greene, J.~L. (2009).
\newblock Ecology of chicken turtles (\emph{Deirochelys reticularia}) in a
  seasonal wetland ecosystem: Exploiting resource and refuge environments.
\newblock {\em Herpetologica}, 65(1):39--53.

\bibitem[Burbidge, 1981]{Burb1981}
Burbidge, A.~A. (1981).
\newblock The ecology of the western swamp tortoise \emph{Pseudemydura umbrina}
  ({T}estudines: {C}helidae).
\newblock {\em Australian Wildlife Research}, 8:203--223.

\bibitem[Burbidge et~al., 2010]{BurbKuch2010}
Burbidge, A.~A., Kuchling, G., Olejnik, C., and Mutter, L. (2010).
\newblock Western swamp tortoise (\emph{Pseudemydura umbrina}) recovery plan,
  4th edition.
\newblock Technical report.

\bibitem[Byrd et~al., 2005]{ByrdMurp2005}
Byrd, J., Murphy, S., and von Harten, A. (2005).
\newblock Morphometric analysis of the northern subpopulation of
  \textit{Caretta caretta} in {S}outh {C}arolina, {U}{S}{A}.
\newblock {\em Marine Turtle Newsletter}, 107:1--4.

\bibitem[Campos et~al., 2013]{CampMahn2013}
Campos, Z., Magnusson, W.~E., and Marques, V. (2013).
\newblock Growth rates of \emph{Paleosuchus palpebrosus} at the southern limit
  of its range.
\newblock {\em Herpetologica}, 69(4):405--410.

\bibitem[Campos et~al., 2008]{CampMagn2008}
Campos, Z., Magnusson, W.~E., Sanaiotti, T., and Coutinho, M. (2008).
\newblock Reproductive trade-offs in \emph{Caiman crocodilus crocodilus} and
  \emph{Caiman crocodilus yacare}: implications for size-related management
  quotas.
\newblock {\em HERPETOLOGICAL JOURNAL}, 18:91--96.

\bibitem[Casale et~al., 2011]{CasaCont2011}
Casale, P., Conte, N., Freggi, D., Cioni, C., and Argano, R. (2011).
\newblock Age and growth determination by skeletochronology in loggerhead sea
  turtles (\textit{Caretta caretta}) from the {M}editerranean sea.
\newblock {\em Scientia Marina}, 75(1):197--203.

\bibitem[Casale et~al., 2009]{CasaPino2009}
Casale, P., dAstore, P.~P., and Argano, R. (2009).
\newblock Age at size and growth rates of early juvenile loggerhead sea turtles
  (\textit{Caretta caretta}) in the {M}editerranean based on length frequency
  analysis.
\newblock {\em Herpetological Journal}, 19:29--33.

\bibitem[Cateau, 2014]{Cate2014}
Cateau, S. (2014).
\newblock personal communication.

\bibitem[\c{C}i\c{c}ek et~al., 2016]{CiceKuma2016}
\c{C}i\c{c}ek, K., Kuma\c{s}, M., Ayaz, D., and Tok, C.~V. (2016).
\newblock A skeletochronological study of age, growth and longevity in two
  freshwater turtles, \emph{Emys orbicularis} and \emph{Mauremys rivulata},
  from {M}editerranean {T}urkey ({R}eptilia: {T}estudines).
\newblock {\em Zoology in the Middle East}.

\bibitem[Chaloupka et~al., 2004]{ChalLimp2004}
Chaloupka, M., Limpus, C., and Miller, J. (2004).
\newblock Green turtle somatic growth dynamics in a spatially disjunct great
  barrier reef metapopulation.
\newblock {\em Coral Reefs}, 23:325--335.

\bibitem[Chen and Lue, 1998]{ChenLue1998}
Chen, T.-H. and Lue, K.-Y. (1998).
\newblock Ecology of the chinese stripe-necked turtle, \emph{Ocadia sinensis}
  ({T}estudines: {E}mydidae), in the {K}eelung {R}iver, {N}orthern {T}aiwan.
\newblock {\em Copeia}, 4:944--952.

\bibitem[Chen and Lue, 2002]{ChenLue2002}
Chen, T.-H. and Lue, K.-Y. (2002).
\newblock Growth patterns of the yellow-margined box turtle (\emph{Cuora
  flavomarginata}) in {N}orthern {T}aiwan.
\newblock {\em Journal of Herpetology}, 36(2):201--208.

\bibitem[Chentanez et~al., 1983]{ChenHugg1983}
Chentanez, T., Huggins, S.~E., and Chentanez, V. (1983).
\newblock Allometric relationships of th {S}iamese crocodile, \emph{Crocodylus
  siamensis}.

\bibitem[Chinsamya and Valenzuela, 2008]{ChinVale2008}
Chinsamya, A. and Valenzuela, N. (2008).
\newblock Skeletochronology of the endangered side-neck turtle,
  \emph{Podocnemis expansa}.
\newblock {\em South African Journal of Science}, 104:311--314.

\bibitem[Christens, 1990]{Chri1990}
Christens, E. (1990).
\newblock Nest emergence lag in loggerhead sea turtles.
\newblock {\em Journal of Herpetology}, 24(4):400--402.

\bibitem[Congdon and van Loben~Sels, 1991]{CongLobe1991}
Congdon, J.~D. and van Loben~Sels, R.~C. (1991).
\newblock Growth and body size in blanding's turtles (\emph{Emydoidea
  blandingi}): relationships to reproduction.
\newblock {\em Can. J. Zool.}, 69:239--245.

\bibitem[Cox et~al., 1991]{CoxHaze1991}
Cox, W.~A., Hazelrig, J.~B., Turner, M.~E., Aangus, R.~A., and Marion, K.~R.
  (1991).
\newblock A model for growth in the musk turtle, \emph{Sternotherus minor}, in
  a {N}orth {F}lorida spring.
\newblock {\em Copeia}, 1991(4):954--968.

\bibitem[Deeming and Ferguson, 1991]{DeemFerg1991}
Deeming, D.~C. and Ferguson (1991).
\newblock {\em Egg incubation; its effects on embryonic development in birds
  and reptiles}.
\newblock Cambridge Univ. Press, Cambridge.

\bibitem[Dobie, 1971]{Dobi1971}
Dobie, J.~L. (1971).
\newblock Reproduction and growth in the alligator snapping turtle,
  \emph{Macroclemys temmincki} (troost).
\newblock {\em Copeia}, 1971(4)(1):645--658.

\bibitem[Doody et~al., 2003]{DoodGeor2003}
Doody, J.~S., Georges, A., and Young, J.~E. (2003).
\newblock Twice every second year: reproduction in the pig-nosed turtle,
  \emph{Carettochelys insculpta}, in the wet-dry tropics of {A}ustralia.
\newblock {\em J. Zool. Lond.}, 259:179--188.

\bibitem[dos Santos~Braga et~al., 2021]{BragFern2021}
dos Santos~Braga, B.~S., Fernandes?Neto, D.~L., Silva, R. P. L. S.~R.,
  Ferreira, M. A.~P., Oliveira?Bahia, V.~R., Marques, J. R.~F., and
  de~Ara\'{u}jo Guimar\~{a}es, D.~A. (2021).
\newblock Embryonic development of \emph{Kinosternon scorpioides}
  ({T}estudines: {K}inosternidae).
\newblock {\em Zoomorphology}.

\bibitem[Dreslik, 1997]{Dres1997}
Dreslik, M.~J. (1997).
\newblock Ecology of the river cooter, \emph{Pseudemys concinna}, in a southern
  {I}llinois floodplain lake.
\newblock {\em Herpetological Natural History}, 5(2):135--145.

\bibitem[Du et~al., 2009]{DuShen2009}
Du, W.-G., Shen, J.-W., and Wang, L. (2009).
\newblock Embryonic development rate and hatchling phenotypes in the {C}hinese
  three-keeled pond turtle (\emph{Chinemys reevesii}): The influence of
  fluctuating temperature versus constant temperature.
\newblock {\em Journal of Thermal Biology}, 34):250--255.

\bibitem[Ehrhart and Yoder, 1978]{EhrhYode1978}
Ehrhart, L.~M. and Yoder, R.~G. (1978).
\newblock Marine turtles of {M}erritt island national wildlife refuge,
  {K}ennedy space center, {F}lorida.
\newblock {\em Florida Marine Research Publication}, 33:25--30.
\newblock Proceedings of the Florida and interregional conference on sea
  turtles, July 1976, Jensen Beach, Florida, USA.

\bibitem[Ekanayake et~al., 2016]{EkanKapu2016}
Ekanayake, E., Kapurusinghe, T., Saman, M., Rathankumara, D., Samaraweera, P.,
  and Rajakaruna, R. (2016).
\newblock Reproductive output and morphometrics of green turtle, \emph{Chelonia
  mydas} nesting at the kosgoda rookery in sri lanka.
\newblock {\em Ceylon Journal of Science}, 45(3):103--116.

\bibitem[Erickson and Brochu, 1999]{EricBroc1999}
Erickson, G.~M. and Brochu, C.~A. (1999).
\newblock How the terror crocodile grew so big.
\newblock {\em Nature}, 398:205--206.

\bibitem[Ernst, 1975]{Erns1975}
Ernst, C.~H. (1975).
\newblock Growth of the spotted turtle, \emph{Clemmys guttata}.
\newblock {\em Journal of Herpetology}, 9(3)):313--318.

\bibitem[Ernst, 1986]{Erns1986}
Ernst, C.~H. (1986).
\newblock Ecology of the turtle, \emph{Sternotherus odoratus}, in southeastern
  {P}ennsylvania.
\newblock {\em Journal of Herpetology}, 20(3):341--352.

\bibitem[Ernst and Barbour, 1989]{ErnsBarb1989}
Ernst, C.~H. and Barbour, R.~W. (1989).
\newblock {\em Turtles of the world}.
\newblock Smithsonian Institutiun Press, Washington.

\bibitem[Ernst et~al., 1998]{ErnsWilg1998}
Ernst, C.~H., Wilgenbusch, J.~C., Boucher, T.~P., and Sekscienski, S.~W.
  (1998).
\newblock Growth, allometry and sexual dimorphism in the {F}lorida box turtle,
  \emph{Terrapene carolina} {B}auri.
\newblock {\em Herpedological Journal}, 8:72--78.

\bibitem[Ewert et~al., 2004]{EwerHatc2004}
Ewert, M.~A., Hatcher, R.~E., and Goode, J.~M. (2004).
\newblock Sex determination and ontogeny in \emph{Malacochersus tornieri}, the
  pancake tortoise.
\newblock {\em Journal of Herpetology}, 38(2):291--295.

\bibitem[Fielder et~al., 2015]{FielLimp2015}
Fielder, D.~P., Limpus, D.~J., and Limpus, C.~J. (2015).
\newblock Reproduction and population ecology of the vulnerable western
  sawshelled turtle, \emph{Myuchelys bellii}, in the {M}urray-{D}arling
  {B}asin, {A}ustralia.
\newblock {\em Australian Journal of Zoology}.

\bibitem[Frazer and Ehrhart, 1985]{FrazEhrh1985}
Frazer, N. and Ehrhart, L. (1985).
\newblock Preliminary growth models for green, \emph{Chelonia mydas}, and
  loggerhead, \emph{Caretta caretta}, turtles in the wild.
\newblock {\em Copeia}, 1985:73--79.

\bibitem[Frazer and Ladner, 1986]{FrazLadn1986}
Frazer, N. and Ladner, R. (1986).
\newblock A growth curve for green sea turtles, \emph{Chelonia mydas}, in the
  us virgin islands, 1913-14.
\newblock {\em Copeia}, 1986(3):789--802.

\bibitem[Frazer et~al., 1990]{FrazGibb1990}
Frazer, N.~B., Gibbons, J.~W., and Greene, J.~L. (1990).
\newblock Exploring fabens' growth interval model with data on a long-lived
  vertebrate, \emph{Trachemys scripta} ({R}eptilia: {T}estudinata).
\newblock {\em Copeia}, 1990(1):112--118.

\bibitem[Gaikhorst et~al., 2011]{GaikClar2011}
Gaikhorst, G.~S., Clarke, B.~R., McPharlin, M., Larkin, B., McLaughlin, J., and
  Mayes, J. (2011).
\newblock The captive husbandry and reproduction of the pink-eared turtle
  (\emph{Emydura victoriae}) at {P}erth {Z}oo.
\newblock {\em Zoo Biology}, 30:79--94.

\bibitem[Garc\'{i}a-Grajales et~al., 2012]{GarcBuen2012}
Garc\'{i}a-Grajales, J., Buenrostro-Silva, A., and Charruau, P. (2012).
\newblock Growth and age of juvenile {A}merican crocodiles (\emph{Crocodylus
  acutus} in la {V}entanilla estuary, {O}axaca, {M}exico.
\newblock {\em Herpetological Conservation and Biology}, 7:330--338.

\bibitem[Gerlach, 2008]{Gerl2008}
Gerlach, J. (2008).
\newblock Fragmentation and demography as causes of population decline in
  {S}eychelles freshwater turtles (genus \emph{Pelusios}).
\newblock {\em Chelonian Conservation and Biology}, 7(1):78--87.

\bibitem[Germano and Riedle, 2015]{GermRied2015}
Germano, D.~J. and Riedle, J.~D. (2015).
\newblock Population structure, growth, survivorship, and reproduction of
  \emph{Actinemys marmorata} from a high elevation site in the {T}ehachapi
  {M}ountains, {C}alifornia.
\newblock {\em Herpetologica}, 71(2):102--109.

\bibitem[Godfrey and Mrosovsky, 1997]{GodfMros1997}
Godfrey, M.~H. and Mrosovsky, N. (1997).
\newblock Estimating the time between hatching of sea turtles and their
  emergence from the nest.
\newblock {\em Chelonian Conservation and Biology}, 2:581--585.

\bibitem[Goetz, 2007]{Goet2007}
Goetz, M. (2007).
\newblock Husbandry and breeding of the spiny turtle \emph{Heosemys spinosa}
  ({G}ray, 1931) at the {D}urrell {W}ildlife {C}onservation {T}rust.
\newblock {\em RADIATA}, 16(2).

\bibitem[Goshe et~al., 2010]{GoshAven2010}
Goshe, L., Avens, L., Scharf, F., and Southwood, A. (2010).
\newblock Estimation of age at maturitaion and growth of atlantic green turtles
  \emph{Chelonia mydas} using skeletochronology.
\newblock {\em Marine Biology}, 157(8):1725--1740.

\bibitem[Graham, 1971]{Grah1971}
Graham, T.~E. (1971).
\newblock Growth rate of the red-bellied turtle, \emph{Chrysemys rubriventris},
  at {P}lymouth, {M}assachusetts.
\newblock {\em Copeia}, 1971(2)):353--356.

\bibitem[Groombridge, 1990]{Groom1990}
Groombridge, B. (1990).
\newblock Marine turtles in the {M}editerranean: distribution, population
  status, and conservation.
\newblock Technical Report~48, {Report to the Council of Europe, Environmental
  Conservation and Management Division}.

\bibitem[Guinea, 2009]{Guin2009}
Guinea, M.~L. (2009).
\newblock Long term marine turtle monitoring at scott reef.
\newblock Unpublished report to Sinclair Knight Merz.

\bibitem[Hairul and Shahrul~Anuar, 2014]{HairShah2014}
Hairul, M. and Shahrul~Anuar, M. (2014).
\newblock Developmental stages of southern river terrapin (\emph{Batagur
  affinis}) in wildlife conversation center {B}ota {K}anan, {P}erak,
  {M}alaysia.
\newblock {\em Journal of Wildlife and Parks}, 28:1--7.

\bibitem[Hawkes et~al., 2005]{HawkBrod2005}
Hawkes, L., Broderick, A., Godfrey, M., and Godley, B. (2005).
\newblock Status of nesting loggerhead turtles \textit{Caretta caretta} at
  {B}ald {H}ead island ({N}orth {C}arolina, {U}{S}{A}) after 24 years of
  intensive monitoring and conservation.
\newblock {\em Oryx}, 39:65--72.

\bibitem[Hays and Speakman, 1991]{HaysSpea1991}
Hays, G.~C. and Speakman, J.~R. (1991).
\newblock Reproductive investment and optimum clutch size of loggerhead sea
  turtles (\textit{Caretta caretta}).
\newblock {\em Journal of Animal Ecology}, 60(2):455--462.

\bibitem[Hendrickson, 1958]{Hend1958}
Hendrickson, J. (1958).
\newblock The green sea turtle, \emph{Chelonia mydas} (linn) in malaya and
  sarawak.
\newblock {\em Journal of Zoology}, 130(4):455--535.

\bibitem[Hensley et~al., 2010]{HensJone2010}
Hensley, F.~R., Jones, T.~R., Maxwell, M.~S., Adams, L.~J., and Nedella, N.~S.
  (2010).
\newblock Demography, terrestrial behavior, and growth of {S}onora mud turtles
  (\emph{Kinosternon sonoriense}) in an extreme habitat.
\newblock {\em Herpetological Monographs}, 24:174--193.

\bibitem[Herbert et~al., 2002]{HerbCoul2002}
Herbert, J., Coulson, T., and Coulson, R. (2002).
\newblock Growth rates of {C}hinese and {A}merican alligators.
\newblock {\em Comparative Biochemistry and Physiology Part A}, 131:909–916.

\bibitem[Herron, 1991]{Herr1991}
Herron, J.~C. (1991).
\newblock Growth rates of black caiman \emph{Melanosuehus niger} and spectacled
  caiman \emph{Caiman crocodilus}, and the recruitment, of breeders in hunted
  caiman populations.
\newblock {\em Biological Conservation}, 55:103--113.

\bibitem[Hichami et~al., 2016]{HichZnar2016}
Hichami, N., Znari, M., Naimi, M., and Namous, S. (2016).
\newblock Clutch, egg and hatchling characteristics in the {S}ouss valley
  tortoises, \emph{Testudo graeca soussensis} {P}ieh, 2001 ({T}estudines:
  {T}estudinidae) from an arid steppe-land of {W}est-{C}entral {M}orocco,
  {A}frica.
\newblock {\em Journal of Herpetology}, 65:21--32.

\bibitem[Hildebrand and Hatsel, 1927]{HildHats1927}
Hildebrand, S.~F. and Hatsel, C. (1927).
\newblock On the growth, care and behavior of loggerhead turtles in captivity.
\newblock {\em Proceedings of the National Academy of Sciences of the United
  States of America}, 13(6):374--377.

\bibitem[Iverson, 1979]{Iver1979}
Iverson, J.~B. (1979).
\newblock Reproduction and growth of the mud turtle, \emph{Kinosteron
  subrubrum} ({R}eptilia, {T}estudines, {K}inosternidae), in {A}rkansas.
\newblock {\em Journal of Herpetology}, 13(1):105--111.

\bibitem[Iverson, 1991]{Iver1991}
Iverson, J.~B. (1991).
\newblock Life history and demography of the yellow mud turtle,
  \emph{Kinosternon flavescens}.
\newblock {\em Herpetologica}, 25(1):373--395.

\bibitem[Iverson, 2010]{Iver2010}
Iverson, J.~B. (2010).
\newblock Reproduction in the red-cheeked mud turtle (\emph{Kinosternon
  scorpioides cruentatum}) in {S}outheastern {M}exico and {B}elize, with
  comparisons across the species range.
\newblock {\em Chelonian Conservation and Biology}, 9(2):250--261.

\bibitem[Iverson et~al., 1991]{IverBart1991}
Iverson, J.~B., Barthelmess, E.~L., Smith, G.~R., and Derivera, C.~E. (1991).
\newblock Growth and reproduction in the mud turtle \emph{Kinosternon hirtipes}
  in chihuahua, mexico.
\newblock {\em Journal of Herpetology}, 25(1):64--72.

\bibitem[Jacobson and Kushlan, 1989]{JacoKush1989}
Jacobson, T. and Kushlan, J.~A. (1989).
\newblock Growth dynamics in the {A}merican alligator (\emph{Alligator
  mississipiensis}).
\newblock {\em J. Zool. Lond.}, 219:309--328.

\bibitem[Ji et~al., 2003]{JiChen2003}
Ji, X., Chen, F., Du, W.-G., and Chen, H.-L. (2003).
\newblock Incubation temperature affects hatchling growth but not sexual
  phenotype in the {C}hinese soft-shelled turtle, \emph{Pelodiscus sinensis}
  ({T}rionychidae).
\newblock {\em J. Zool., Lond.}, 261:409--416.

\bibitem[Jones, 2003]{Jone2003}
Jones, G. (2003).
\newblock Technical report, The Cooperative Research Centre for Freshwater
  Ecology.

\bibitem[Jones and Hartfield, 1995]{JoneHart1995}
Jones, R.~L. and Hartfield, P.~D. (1995).
\newblock Population size and growth in the turtle \emph{Graptemys oculifera}.
\newblock {\em Journal of Herpetology}, 29(3):426--436.

\bibitem[Jones, 2009]{Jone2009}
Jones, T.~T. (2009).
\newblock {\em Energetics of the leatherback turtle, \emph{Dermochelys
  coriacea}}.
\newblock PhD thesis, Univ Britisch columbia (Vancouver).

\bibitem[Judd and McQueen, 1980]{JuddMcQu1980}
Judd, F.~W. and McQueen, J.~C. (1980).
\newblock Incubation, hatching, and growth of the tortoise, \emph{Gopherus
  berlandieri}.
\newblock {\em Journal of Herpetology}, 14(4):377--380.

\bibitem[Kanwatakid-Savini et~al., 2012]{PlatNomy2012}
Kanwatakid-Savini, P., Pliosungnoen, M., Pattanavibool, A., Thorbjarnarson,
  J.~B., Limlikhitaksorn, C., and Platt, S.~G. (2012).
\newblock A survey to determine the conservation status of {S}iamese crocodiles
  in {K}aeng {K}rachan {N}ational {P}ark, {T}hailand.
\newblock {\em Herpetological Conservation and Biology}, 7(2):157–168.

\bibitem[Kennett, 1996]{Kenn1996}
Kennett, R. (1996).
\newblock Growth models for two species of freshwater turtle, \emph{Chelodina
  rugosa} and \emph{Elseya dentata} from the wet-dry tropics of {N}orthern
  {A}ustralia.
\newblock {\em Herpetologica}, 50(3):383--395.

\bibitem[Keswick, 2012]{Kesw2012}
Keswick, T. (2012).
\newblock {\em Ecology and morphology of the {K}alahari tent tortoise,
  \emph{Psammobates oculifer}, in a semi-arid environment}.
\newblock PhD thesis, University of the Western Cape.

\bibitem[K.S. et~al., 2014]{VanHHarg2014}
K.S., V.~H., Hargrove, S., and Balazs, G. (2014).
\newblock Modelling sea turtle maturity age from partial life history records.
\newblock {\em Pacific Science}, 68(4):465--477.

\bibitem[Kumar et~al., 2010]{KumaHari2010}
Kumar, R.~S., Harihar, A., and Pandav, B. (2010).
\newblock Population characteristics of a terrestrial geoemydid,
  \emph{Melanochelys tricarinata}, from the {D}oon {V}alley, northern {I}ndia.
\newblock {\em Herpetological Journal}, 20:139--146.

\bibitem[Legler and Vogt, 2013]{LeglVogt2013}
Legler, J.~M. and Vogt, R.~C. (2013).
\newblock {\em Turtles of Mexico; land and freshwater forms}.
\newblock Univ. of Calif. Press, Berkeley.

\bibitem[Leshem et~al., 1991]{LeshAr1991}
Leshem, A., Ar, A., and Ackerman, R.~A. (1991).
\newblock Growth, water, and energy metabolism of the soft-shelled
  turtle(\emph{Trionyx triunguis}) embryo: Effects of temperature.
\newblock {\em Physiological Zoology}, 64(2):568--594.

\bibitem[Limpus, 1993]{Limp1993}
Limpus, C. (1993).
\newblock The green turtle,\emph{Chelonia mydas}, in queensland: breeding males
  in the southern great barrier reef.
\newblock {\em Wildlife Research}, 20(4):513--523.

\bibitem[Limpus, 2007]{Limp2007}
Limpus, C. (2007).
\newblock A biological review of {A}ustralian marine turtle species. 5.
  {F}latback turtle, \textit{Natator depressus}, ({G}arman).
\newblock Technical report, Queensland Government Environmental Protection
  Agency: Brisbane.

\bibitem[Limpus, 2008]{Limp2008}
Limpus, C. (2008).
\newblock Freshwater turtles in the {M}ary {R}iver: {R}eview of biological data
  for turtles in the {M}ary {R}iver, with emphasis on \emph{Elusor macrurus}
  and \emph{Elseya albagula}.
\newblock Technical report, Brisbane: Queensland Government.

\bibitem[Limpus and Fien, 2009]{Limp2009}
Limpus, C. and Fien, L. (2009).
\newblock {\em A Biological Review of Australian Marine Turtles}.
\newblock Environmental Protection Agency.

\bibitem[Limpus and Nicholls, 1988]{LimpNich1988}
Limpus, C. and Nicholls, N. (1988).
\newblock The southern oscillation regulates the annual numbers of green
  turtles (\emph{Chelonia mydas}) breeding around northern australia.
\newblock {\em Wildlife Research}, 15(2):157--161.

\bibitem[Limpus et~al., 2005]{LimpMill2003}
Limpus, C.~J., Limpus, D.~J., Arthur, K., and Parmenter, J.~C. (2005).
\newblock Monitoring green turtle population dynamics in shoalwater bay:
  2000-2004.
\newblock Technical Report~83, Queensland Environmenal Protection Agency.

\bibitem[Lindeman, 1999]{Lind1999}
Lindeman, P.~V. (1999).
\newblock Growth curves for \emph{Graptemys}, with a comparison to other emydid
  turtles.
\newblock {\em Am. Midl. Nat.}, 142:141--151.

\bibitem[Lindeman, 2005]{Lind2005}
Lindeman, P.~V. (2005).
\newblock Aspects of the life history of the texas map turtle (\emph{Graptemys
  versa}).
\newblock {\em Am. Midl. Nat.}, 153:378--388.

\bibitem[Lindeman, 2007]{Lind2007}
Lindeman, P.~V. (2007).
\newblock Diet, growth, body size, and reproductive potential of the {T}exas
  river cooter (\emph{Pseudemys texana}) in the south {L}lano {R}iver, {T}exas.
\newblock {\em THE SOUTHWESTERN NATURALIST}, 52(4):586--594.

\bibitem[Loehr, 2004]{Loeh2004}
Loehr, V.~J. (2004).
\newblock Growth of the {N}amaqualand speckled padloper, \emph{Homopus signatus
  signatus} ({R}eptilia: {T}estudinidae).
\newblock {\em African Zoology}, 39(2):309--313.

\bibitem[Lovich et~al., 1998]{LoviErns1998}
Lovich, J.~E., Ernst, C.~H., Zappalort, R.~T., and Harman, D.~W. (1998).
\newblock Geographic variation in growth and sexual size dimorphism of bog
  turtles (\emph{Clemmys muhlenbergii}).
\newblock {\em Am. Midl. Nat.}, 139):69--78.

\bibitem[Magalh\={a}es et~al., 2017]{MagaVogt2017}
Magalh\={a}es, M.~S., Vogt, R.~C., Sebben, A., Dias, L.~C., de~Oliveira, M.~F.,
  and de~Moura, C. E.~B. (2017).
\newblock Embryonic development of the giant {S}outh {A}merican river turtle,
  \emph{Podocnemis expansa} ({T}estudines: {P}odocnemididae).
\newblock {\em Zoomorphology}, 136:523--537.

\bibitem[Magnusson et~al., 1997]{MagnLima1997}
Magnusson, W.~E., de~Lima, A.~C., de~Costa, V.~L., and de~Lima, O.~P. (1997).
\newblock Growth of the turtle, \emph{Phrynops rufipes} in central
  {A}maz\^{o}nia, {B}razil.
\newblock {\em Chelonian Conservation and Biology}, 2(4):78--87.

\bibitem[Marchand et~al., 2018]{MarcHugh2018}
Marchand, K.~A., Hughes, G.~N., and Litzgus, J.~D. (2018).
\newblock Geographic variation in somatic growth rate of wood turtles
  (\emph{Glyptemys insculpta}).
\newblock {\em Copeia}, 106(3):477--484.

\bibitem[Margaritoulis et~al., 2003]{MargArga2003}
Margaritoulis, D., Argano, R., Baran, I., Bentivegna, F., Bradai, M., Caminas,
  J., Casale, P., Metrio, G.~D., A.Demetropoulos, Gerosa, G., Godley, B.,
  Haddoud, D., Houghton, J., Laurent, L., and Lazar, B. (2003).
\newblock Loggerhead turtles in the {M}editerranean sea: Present knowledge and
  conservation perspectives.
\newblock In Bolten, A. and Witherington, B., editors, {\em Loggerhead Sea
  Turtles}, pages 175--198. Smithsonian Books, Washington D.C.

\bibitem[Markham and Kirkwood, 1988]{MarkKirk1988}
Markham, J. and Kirkwood, J.~K. (1988).
\newblock Rearing the olve ridley \emph{Lepidochelys olivacea} hand-reared at
  the {London zoo}.
\newblock {\em Int. Zoo Yb.}, 27:316--319.

\bibitem[Martins and Souza, 2008]{MartSouz2008}
Martins, F.~I. and Souza, F.~L. (2008).
\newblock Estimates of growth of the {A}tlantic rain forest freshwater turtle
  \emph{Hydromedusa maximiliani} ({C}helidae).
\newblock {\em Journal of Herpetology}, 42(1):54--60.

\bibitem[Marzola et~al., 2014]{MarzRuss2014}
Marzola, M., Russo, J., and Mateus, O. (2014).
\newblock Identification and comparison of modern and fossil crocodilian eggs
  and eggshell structures.
\newblock {\em Historical Biology}.

\bibitem[Masin et~al., 2015]{MasiFice2015}
Masin, S., Ficetola, G.~F., and Bottoni, L. (2015).
\newblock Head starting european pond turtle (\emph{Emys orbicularis}) for
  reintroduction: Patterns of growth rates.
\newblock {\em Herpetological Conservation and Biology},
  10(Symposium):516--524.

\bibitem[Medica et~al., 2012]{MediNuss2012}
Medica, P.~A., Nussear, K.~E., Esque, T.~C., and Saethre, M.~B. (2012).
\newblock Long-term growth of desert tortoises (\emph{Gopherus agassizii}) in a
  southern {N}evada population.
\newblock {\em Journal of Herpetology}, 46(2):213--220.

\bibitem[Meers et~al., 2016]{MeerRobi2016}
Meers, M.~B., Robinson, K.~L., Smith, D., Scordino, A., and Fisher, L. (2016).
\newblock Effect of diet on growth in captive \emph{Podocnemis unifilis}:
  assessing optimal diets for turtles in head-starting programs.
\newblock {\em Bullitin Florida Museum Natural History}, 54(4):58--68.

\bibitem[Melancon et~al., 2011]{MelaAngu2011}
Melancon, S.~R., Angus, R.~A., and Marion, K.~R. (2011).
\newblock Growth of the flattened musk turtle, \emph{Sternotherus depressus}
  {T}inkle and {W}ebb.
\newblock {\em Southeastern Naturalist}, 10(3):399--408.

\bibitem[Miller et~al., 2003]{MillLimp2003}
Miller, J.~D., Limpus, C.~L., and Godfrey, M.~H. (2003).
\newblock Nest site selection, oviposition, eggs, development, hatching, and
  emergence of loggerhead sea turtles.
\newblock In Bolten, A. and Witherington, B., editors, {\em Ecology and
  Conservation of Loggerhead Sea Turtles}, pages 125--143. University Press of
  Florida, Gainesville, Florida.

\bibitem[Miorando et~al., 2015]{MiorGiar2016}
Miorando, P.~S., Giarrizzo, T., and Pezzuti, J. C.~B. (2015).
\newblock Population structure and allometry of \emph{Podocnemis unifilis}
  ({T}estudines, {P}odocnemididae) in a protected area upstream {B}elo {M}onte
  dam in {X}ingu {R}iver, {B}razil.
\newblock {\em Anais da Academia Brasileira de Ci\^{e}ncias}, 87(4):2067--2079.

\bibitem[Miranda et~al., 2002]{MiraMora2002}
Miranda, M.~P., de~Moraes, G.~V., Martins, E.~N., Maia, L. C.~P., and Barbosa,
  O.~R. (2002).
\newblock Thermic variation in incubation and development of {P}antanal caiman
  (\emph{Caiman crocodilus yacare}) ({D}audin, 1802) kept in metabolic box.
\newblock {\em Brazilian Archives of Biology and Technology},
  45:http://dx.doi.org/10.1590/S1516--89132002000300012.

\bibitem[Moll et~al., 2015]{MollPlatt2015}
Moll, E.~O., Platt, S.~G., Chan, E.~H., Horne, B.~D., Platt, K., Praschag, P.,
  Chen, P.~N., and van Dijk, P.~P. (2015).
\newblock \emph{Batagur affinis} ({C}antor 1847) - {S}outhern {R}iver
  {T}errapin, {T}untong.
\newblock Technical report, Chelonian Research Foundation.

\bibitem[Moreira et~al., 1995]{MoreBapt1995}
Moreira, L., Baptistotte, C., Scalfone, J., Thom, J., and De~Almeida, A.
  (1995).
\newblock Occurrence of \emph{Chelonia mydas} on the island of trindade,
  brazil.
\newblock {\em Marine Turtle Newsletter}, 70(2).

\bibitem[Mourao et~al., 2014]{CampMour2014}
Mourao, Z. C.~G., Coutinho, M., and Magnusson, W.~E. (2014).
\newblock Growth of \emph{Caiman crocodilus yacare} in the {B}razilian
  {P}antanal.
\newblock {\em Plos One}, 9(2):e89363.

\bibitem[Munscher et~al., 2015]{MunsWald2015}
Munscher, E.~C., Walde, A.~D., Stratmann, T., , and Butterfield, B.~P. (2015).
\newblock Exceptional growth rates observed in immature \emph{Pseudemys} from a
  protected spring system in {F}lorida.
\newblock {\em Herpetology Notes, volume}, 8:133--140.

\bibitem[Mushinsky et~al., 1994]{MushWils1994}
Mushinsky, J. H.~R., Wilson, D.~S., and McCoy, E.~D. (1994).
\newblock Growth and sexual dimorphism of gopherus polyphemus in central
  {F}lorida.
\newblock {\em Herpetologica}, 50(2):119--128.

\bibitem[Ngwanya et~al., 2013]{NgwePatz2013}
Ngwanya, A., Patzke, N., Sprocter, M.~A., Kruger, J.-L., Dell, L.-A., Chawana,
  R., Mazengenya, P., Billings, B.~K., Olaleye, O., Herculano-Houzel, S., and
  Manger, P.~R. (2013).
\newblock The continuously growing central nervous system of the {N}ile
  crocodile (\emph{Crocodylus niloticus}).
\newblock {\em The Anatomical Record}, 296:1489--1500.

\bibitem[Norton, 2005]{Nort2005}
Norton, T.~M. (2005).
\newblock Sea turtle conservation in {G}eorgia and an overview of the {G}eorgia
  sea turtle center on {J}ekyll island, {G}eorgia.
\newblock {\em Georgia Journal of Science}, 63:287--289.

\bibitem[Novelli and de~Sousa, 2008]{NoveSous2008}
Novelli, I.~A. and de~Sousa, B.~M. (2008).
\newblock \emph{Hydromedusa maximiliani} ({B}razilian snake-necked turtle).
  {H}atchling size and body mass.
\newblock {\em Herpetological Review}, 39(3):344--345.

\bibitem[P\'{a}aez et~al., 2015]{PaezBock2015}
P\'{a}aez, V.~P., Bock, B.~C., Espinal-Garc\'{i}, P.~A., Rend\'{o}n-Valencia,
  B.~H., Alzate-Estrada, D., Cartagena-Ot\'{a}lvaro, V.~M., and Heppel, S.~S.
  (2015).
\newblock Life history and demographic characteristics of the {M}agdalena river
  turtle (\emph{Podocnemis lewyana}): {I}mplications for management.
\newblock {\em Copeia}, 103:1058--1074.

\bibitem[P\'{a}ez et~al., 2009]{PaezCorr2009}
P\'{a}ez, V.~P., Correa, J.~C., Cano, A.~M., and Bock, B.~C. (2009).
\newblock A comparison of maternal and temperature effects on sex, size, and
  growth of hatchlings of the {M}agdalena river turtle (\emph{Podocnemis
  lewyana}) incubated under field and controlled laboratory conditions.
\newblock {\em Copeia}, 2009:698--704.

\bibitem[Parker, 1926]{Park1926}
Parker, G.~H. (1926).
\newblock The growth of turtles.
\newblock {\em Proceedings of the National Academy of Sciences},
  12(7):422--424.

\bibitem[Parker, 1929]{Park1929}
Parker, G.~H. (1929).
\newblock The growth of the loggerhead turtle.
\newblock {\em The American Naturalist}, 63(687):367--373.

\bibitem[Pereia et~al., 2011]{PereBoot2011}
Pereia, C., Booth, D., and Limpus, C. (2011).
\newblock Locomotor activity during the frenzy swim: analysig early swimming
  behaviour in hatchling sea turtles.
\newblock {\em Journal of Experimental Biology}, 214(23):3972--3976.

\bibitem[P\'{e}rez-Higareda et~al., 1995]{PereRang1995}
P\'{e}rez-Higareda, G., Rangel-Rangel, A., Chiszar, G., and Smith, H.~M.
  (1995).
\newblock Growth of {M}orelet's crocodile (\emph{Crocodylus moreletii}) during
  the first three years of life.
\newblock {\em Zoo Biology}, 14:173--177.

\bibitem[Piovano et~al., 2011]{PiovClus2011}
Piovano, S., Clusa, M., Carreras, C., Giacoma, C., Pascual, M., and Cardona, L.
  (2011).
\newblock Different growth rates between loggerhead sea turtles
  (\textit{Caretta caretta})of {M}editerranean and {A}tlantic origin in the
  {M}editerranean sea.
\newblock {\em Marine Biology}, 158(11):2577--2587.

\bibitem[Plummer, 1977]{Plum1977}
Plummer, M.~V. (1977).
\newblock Reproduction and growth in the turtle \emph{Trionyx muticus}.
\newblock {\em Copeia}, 1977(3):440--447.

\bibitem[Plummer and Mills, 2015]{PlumMill2015}
Plummer, M.~V. and Mills, N.~E. (2015).
\newblock Growth and maturity of spiny softshell turtles (\emph{Apalone
  spinifera}) in a small urban stream.
\newblock {\em Herpetological Conservation and Biology}, 10(2):688--694.

\bibitem[Prince, 2017]{Prin2017}
Prince, R. (2017).
\newblock personal communication.

\bibitem[Prithard, 2008]{Prit2008}
Prithard, P. C.~H. (2008).
\newblock \emph{Chelus frimbriata} ({S}chneider 1783) - matamata turtle.
\newblock In Rhodin, A. G.~J., Pritchard, P. C.~H., van Dijk, P.~P., Saumure,
  R.~A., Buhlmann, K.~A., and Iverson, J.~B., editors, {\em Conservation
  Biology of Freshwater Turtles and Tortoises: A Compliation Project of the
  IUCN/SSC Tortoise and Freshwater Turtle Specialist Group}, volume~5.
  Chelonian Research Foundation and Turtle Conservation; Chelonian Research
  Monographs.

\bibitem[Reich et~al., 2008]{ReicBjor2008}
Reich, K.~J., Bjorndal, K.~A., and del Rio, C.~M. (2008).
\newblock Effects of growth and tissue type on the kinetics of 13{C} and 15{N}
  incorporation in a rapidly growing ectotherm.
\newblock {\em Oecologia}, 155:651--663.

\bibitem[Reid et~al., 2009]{ReidMarg2009}
Reid, K.~A., Margaritoulis, D., and Speakman, J.~R. (2009).
\newblock Incubation temperature and energy expenditure during development in
  loggerhead sea turtle embryos.
\newblock {\em Journal of Experimental Marine Biology and Ecology}, 378:62--68.

\bibitem[Ritz et~al., 2012]{RitzClau2012}
Ritz, J., Clauss, M., Streich, W.~J., and Hatt, J.-M. (2012).
\newblock Variation in growth and potentially associated health status in
  {H}ermann's and spur-thighed tortoise (\emph{Testudo hermanni} and
  \emph{Testudo graeca}).
\newblock {\em Zoo Biology}, 31:705--717.

\bibitem[Ritz et~al., 2010a]{RitzGrieb2010}
Ritz, J., Griebeler, E.~M., Huber, R., and Clauss, M. (2010a).
\newblock Body size development of captive and free-ranging {A}frican spurred
  tortoises (\emph{Geochelone sulcata}): high plasticity in reptilian growth
  rates.
\newblock {\em Herpetological Journal}, 20:213--216.

\bibitem[Ritz et~al., 2010b]{RitzHamm2010}
Ritz, J., Hammer, C., and Clauss, M. (2010b).
\newblock Body size development of captive and free-ranging leopard tortoises
  (\emph{Geochelone pardalis}).
\newblock {\em Zoo Biology}, 29:517--525.

\bibitem[Roosenburg and Kelley, 1996]{RoosKell1996}
Roosenburg, W.~M. and Kelley, K.~C. (1996).
\newblock The effect of egg size and incubation temperature on growth in the
  turtle, \emph{Malaclemys terrapin}.
\newblock {\em Journal of Herpetology}, 30(2):198--204.

\bibitem[Rowe, 1994]{Rowe1994}
Rowe, J.~W. (1994).
\newblock Reproductive variation and the egg size-clutch size trade-off within
  and among populations of painted turtles (\emph{Chrysemys picta bellii}).
\newblock {\em Oecologia}, 99:35--44.

\bibitem[Rusli et~al., 2016]{RuslBoot2016}
Rusli, M., Booth, D., and Joseph, J. (2016).
\newblock Synchronous activity lowers the energetic cost of nest escapt for sea
  turtle hatchlings.
\newblock {\em Journal of Experimental Biology}, 219(10):1505--1513.

\bibitem[Salmon, 2017]{Salm2017}
Salmon, M. (2017).
\newblock Turtles reared from hatching at AQWA, Perth by Mike Salmon and
  Jeanette Wyneken.

\bibitem[Salmon et~al., 2009]{SalmHama2009}
Salmon, M., Hamann, M., Wyneken, J., and Schauble, C. (2009).
\newblock Early swimming activity by hatchling flatback sea turtles
  \emph{Natator depressus}: a test of the "predation risk" hypothesis.
\newblock {\em Endangered Species Research}, 9:41--47.

\bibitem[Scott et~al., 2012]{ScotMars2012}
Scott, R., Marsh, R., and Hays, G.~C. (2012).
\newblock Life in the really slow lane: loggerhead sea turtles mature late
  relative to other reptiles.
\newblock {\em Functional Ecology}, 26(1):227--235.

\bibitem[Skorczewski and Andersen, 2021]{SkorAnde2021}
Skorczewski, T. and Andersen, B. (2021).
\newblock A dynamic energy budget model of ornate box turtle shell growth.
\newblock {\em Spora}, 7(2):8--16.

\bibitem[Smith et~al., 2001]{SmitPedr2001}
Smith, L.~L., Pedrono, M., Dorazio, R.~M., and Bishko, J. (2001).
\newblock Morphometrics, sexual dimorphism, and growth in the {A}ngonoka
  tortoise (\emph{Geochelone yniphora}) of western {M}adagascar.
\newblock {\em African Journal of Herpetology}, 50(1):9--18.

\bibitem[Snover et~al., 2007]{SnovAven2007}
Snover, M.~L., Avens, L., and Hohn, A.~A. (2007).
\newblock Back-calculating length from skeletal growth marks in loggerhead sea
  turtles \textit{Caretta caretta}.
\newblock {\em Endang Species Res}, 3:95--104.

\bibitem[Spencer, 2002]{Spen2002}
Spencer, R.-J. (2002).
\newblock Growth patterns in two widely distributed freshwater turtles and a
  comparison of methods used to estimate age.
\newblock {\em Austr. J. Zool.}, 50:477--490.

\bibitem[Spotila, 2004]{Spot2004}
Spotila, J.~R. (2004).
\newblock {\em Sea Turtles: A Complete Guide to their Biology, Behavior, and
  Conservation}.
\newblock The Johns Hopkins University Press and Oakwood Arts., Baltimore,
  Maryland.

\bibitem[Stokes, 2014]{Stok2014}
Stokes, L. (2014).
\newblock personal communication.

\bibitem[Stokes et~al., 2006]{StokWyne2006}
Stokes, L., Wyneken, J., Crowder, L.~B., and Marsh, J. (2006).
\newblock The influence of temporal and spatial origin on size and early growth
  rates in captive loggerhead sea turtles (\textit{Caretta caretta}) in the
  {U}nited {S}tates.
\newblock {\em Herpetological Conservation and Biology}, 1:71--80.

\bibitem[Stoneburner, 1980]{Ston1980}
Stoneburner, D.~L. (1980).
\newblock Body depth: An indicator of morphological variation among nesting
  groups of adult loggerhead sea turtles (\textit{Caretta caretta}).
\newblock {\em Journal of Herpetology}, 14(2):205--206.

\bibitem[Strydom, 2001]{Stry2001}
Strydom, A.~V. (2001).
\newblock {\em Seasonal reproduction and sexual size dimorphism of the
  {A}frican Helmeted Turtle, \emph{Pelomedusa subrufa} (Family
  {P}elomedusidae)}.
\newblock PhD thesis, Univ. of Stellenbosch.

\bibitem[Stubbs et~al., 2019]{StubMitc2019}
Stubbs, J.~L., Mitchell, N.~J., Marn, N., Vanderklift, M.~A., Pillans, R.~D.,
  and Augustine, S. (2019).
\newblock A full life cycle dynamic energy budget ({D}{E}{B}) model for the
  green sea turtle (\emph{Chelonia mydas}) fitted to data on embryonic
  development.
\newblock {\em Journal of Sea Research}, 143:78--88.

\bibitem[Sung et~al., 2014]{SungHau2014}
Sung, Y.-H., Hau, B. C.~H., and Karraker, N.~E. (2014).
\newblock Reproduction of endangered big-headed turtle, \emph{Platysternon
  megacephalum} ({R}eptilia: {T}estudines: {P}latysternidae.
\newblock {\em Acta Herpetologica}, 9(2):243--247.

\bibitem[Sung et~al., 2015]{SungHau2015}
Sung, Y.-H., Hau, B. C.~H., Lau, M. W.~N., Crow, P.~A., Kendrick, R.~C.,
  Buhlmann, K.~A., Ades, G. W.~J., and Karraker, N.~E. (2015).
\newblock Growth rate and an evaluation of age estimation for the endangered
  big-headed turtle (\emph{Platysternon megacephalum}) in {C}hina.
\newblock {\em Journal of Herpetology}, 49(1):99--103.

\bibitem[Targarona et~al., 2010]{TargSobe2010}
Targarona, R.~R., Sober\'{o}n, R.~R., Tabet, M.~A., and Thorbjarnarson, J.~B.
  (2010).
\newblock Cuban crocodile \emph{Crocodylus rhombifer}.
\newblock In Manolis, S. and Stevenson, C., editors, {\em Crocodiles. Status
  Survey and Conservation Action Plan}. Crocodile Specialist Group: Darwin.

\bibitem[Tiwari and Bjorndal, 2000]{TiwaBjor2000}
Tiwari, M. and Bjorndal, K.~A. (2000).
\newblock Variation in morphology and reproduction in loggerheads,
  \textit{Caretta caretta}, nesting in the {U}nited {S}tates, {B}razil, and
  {G}reece.
\newblock {\em Herpetologica}, 56(3):343--356.

\bibitem[Troeng and Chaloupka, 2007]{TroeChal2007}
Troeng, S. and Chaloupka, M. (2007).
\newblock Variation in adult annual survival probability and remigration
  intervals of sea turtles.
\newblock {\em Marine Biology}, 151(5):1721--1730.

\bibitem[Tucker, 2010]{Tuck2010}
Tucker, A.~D. (2010).
\newblock Nest site fidelity and clutch frequency of loggerhead turtles are
  better elucidated by satellite telemetry than by nocturnal tagging efforts:
  Implications for stock estimation.
\newblock {\em Journal of Experimental Marine Biology and Ecology}, 383:48--55.

\bibitem[Venkatesan et~al., 2005]{VenkKann2005}
Venkatesan, S., Kannan, P., Rajagopalan, M., and Vivekanandan, E. (2005).
\newblock Embryonic energetics in the egg of the green turtle \emph{Chelonia
  mydas}.
\newblock {\em Journal of the Marine Biological Association of India},
  47(2):193--197.

\bibitem[Viotto et~al., 2020]{ViotNava2020}
Viotto, E.~V., Navarro, J.~L., and {n}a, C. I.~P. (2020).
\newblock Growth curves of wild and reintroduced broad‑snouted caimans
  (\emph{Caiman latirostris}) and their management implications.
\newblock {\em South American Journal of Herpetology}, 16:34–41.

\bibitem[Vyas, 1979]{Vyas1979}
Vyas, R. (1979).
\newblock Notes on growth and maturity in the {I}ndian roofed turtle
  (\emph{Kachuga tecta}).
\newblock {\em Bombay Natural Hist, Society}, 94):160--162.

\bibitem[Vyas, 1997]{Vyas1997}
Vyas, R. (1997).
\newblock Notes on the growth and maturity of the {I}ndian star tortoise
  (\emph{Geochelone elegans}).
\newblock {\em Zoo's Print}, 12(1):6--7.

\bibitem[Waayers and Stubbs, 2016]{Waay2016}
Waayers, D. and Stubbs, J. (2016).
\newblock A decade of monitoring flatback turtles in {P}ort {H}edland,
  {W}estern {A}ustralia, 2004/05 - 2013/14.
\newblock Technical report.

\bibitem[Wabnitz and Pauly, 2008]{WabnPaul2008}
Wabnitz, C. and Pauly, D. (2008).
\newblock Length-weight relationships and additional growth parameters for sea
  turtles.
\newblock In Palomares, M. L.~D. and Pauly, D., editors, {\em Von Bertalanffy
  growth parameters of non-fish marine organisms}, volume~16 of {\em 10}, page
  138. Fisheries centre research report.

\bibitem[Webb et~al., 1986]{WebbChoq1986}
Webb, G. J.~W., Choqeunot, D., and Whitehead, P.~J. (1986).
\newblock Nests, eggs, and embryonic development of \emph{Carettochelys
  insculpta} ({C}helonia: {C}arettochelidae) from {N}orthern {A}ustralia.
\newblock {\em J. Zool. (Lond.) B}, 1:521--550.

\bibitem[Webb, 1961]{Webb1961}
Webb, R.~G. (1961).
\newblock Observations on the life histories of turtles (genus \emph{Pseudemys}
  and \emph{Graptemys}) in {L}ake {T}exoma, {O}klahoma.
\newblock {\em The American Midland Naturalist}, 65(1):193--214.

\bibitem[Weissenbacher et~al., 2015]{WeisPrei2015}
Weissenbacher, A., Preininger, D., Ghosh, R., Morshed, A. G.~J., and Praschag,
  P. (2015).
\newblock Conservation breeding of the {N}orthern river terrapin \emph{Batagur
  baska} at the {V}ienna {Z}oo, {A}ustria, and in {B}angladesh.
\newblock {\em Int. Zoo Yb.}, 49:31--41.

\bibitem[{Western Australian Department of Biodiversity, Conservation and
  Attractions}, 2019]{DBCA2019}
{Western Australian Department of Biodiversity, Conservation and Attractions}
  (2019).

\bibitem[Whitehead, 1987]{Whit1987}
Whitehead, P.~J. (1987).
\newblock Respiration of \emph{Crocodylus johnstoni} embryos.
\newblock In Webb, G. J.~W., Manolis, S.~C., and Whitehead, P.~J., editors,
  {\em Crocodiles and Alligators}, pages 473--497. Beatty, Sydney.

\bibitem[Whitehead et~al., 1990]{WhitWebb1990}
Whitehead, P.~J., Webb, G. J.~W., and Seymour, R.~S. (1990).
\newblock Effect of incubation temperature on development of \emph{Crocodylus
  johnstoni} embryos.
\newblock {\em Physiol. Zool.}, 63:949--964.

\bibitem[Wilbur, 1975]{Wilb1975}
Wilbur, H.~M. (1975).
\newblock A growth model for the turtle \emph{Chrysemys picta}.
\newblock {\em Copeia}, 1975(2):78--87.

\bibitem[Williamson et~al., 1989]{WilliSpot1989}
Williamson, L.~U., Spotila, J.~R., and Standora, E.~A. (1989).
\newblock Growth, selected temperature and {C}{T}{M} of young snapping turtles,
  \emph{Chelydra serpentina}.
\newblock {\em J. therm. Biol.}, 14(1):33--39.

\bibitem[Wine, 2016]{Wine2016}
Wine, C. (2016).
\newblock Sea turtle energectis.
\newblock {\em Hohonu}, 14:82--88.

\bibitem[Witzell, 1980]{Witz1980}
Witzell, W.~N. (1980).
\newblock Growth of captive hawsbill turtles, \emph{Eretmochelys imbricata}, in
  western {S}amoa.
\newblock {\em Bull. Mar. Sci.}, 30(4):909--912.

\bibitem[Y., 2016]{Seij2016}
Y., A. E.~S. (2016).
\newblock Regional differences in growth rates of {O}rinoco crocodiles
  (\emph{Crocodylus intermedius}) from the {V}enezuelan {L}lanos.
\newblock {\em Herpetological Journal}, 26:263–269.

\bibitem[Yabe, 1989]{Yabe1989}
Yabe, T. (1989).
\newblock Population structure and growth of the {J}apanese pond turtle,
  \emph{Mauremys japonica}.
\newblock {\em Japanese Journal of Herpetology}, 13(1):7--9.

\bibitem[Yntema, 1978]{Ynte1978}
Yntema, C.~L. (1978).
\newblock Incubation times for eggs of the turtle \emph{Chelydra serpentina}
  ({T}estudines: {C}helydridae) at various temperatures.
\newblock {\em Herpetologica}, 34(3):274--277.

\bibitem[Zbinden et~al., 2006]{ZbinMarg2006}
Zbinden, J.~A., Margaritoulis, D., and Arlettaz, R. (2006).
\newblock Metabolic heating in {M}editerranean loggerhead sea turtle clutches.
\newblock {\em Journal of Experimental Marine Biology and Ecology},
  334:151--157.

\bibitem[Zug et~al., 1986]{ZugWynn1986}
Zug, G.~R., Wynn, A.~H., and Ruckdeschel, C. (1986).
\newblock Age determination of loggerhead sea turtles, \textit{Caretta
  caretta}, by incremental growth marks in the skeleton.
\newblock {\em Smithsonian contribution to zoology}, 427.

\bibitem[Zurita et~al., 2012]{ZuriHerr2012}
Zurita, J., Herrera, R., Arenas, A., Negrete, A., Gomez, L., Prezas, B., and
  Sasso, C. (2012).
\newblock Age at first nesting of green turtles in the mexican caribbean.
\newblock In {\em Proceedings of the thirty-first annual symposium on sea
  turtle biology and conservation}, page~75, Miami, Florida. National Oceanic
  and Atmospheric Administration Fisheries Service, Southeast Fisheries Science
  Centre.

\end{thebibliography}


\end{document}